% old
% \begin{abstract}
% In-network computing (INC) has been a fundamental building block that accelerates computing tasks by offloading them to data plane switches. However, existing INC frameworks often include massive \emph{INC task copies} (i.e., replicating task components inside or across switches) to ensure execution correctness, leading to unnecessary switch resource consumption. 

% We propose \sysname, the \underline{R}esource-efficient \underline{INC} framework. Its key idea is to decrease INC task copies: \sysname replaces the sub-optimal manual decomposition of INC tasks with automatic decomposition that reduce inter-switch task copies via careful task analysis. Then it encodes constraints based on the characteristics of modern switches to eliminate intra-switch task copies. We have implemented \sysname on Tofino switches. Our experiments present that compared to state of the arts, \sysname can improve resource efficiency by 61\%. Also, applying \sysname to edge cloud networks built by a global service provider and an Internet service provider helps administrators deploy 0.7$\sim$5.1$\times$ more INC tasks. 
% \end{abstract}

% new
\begin{abstract}
In-network computing (INC) has been a fundamental building block that accelerates computing tasks by offloading them to data plane switches. However, existing INC frameworks often include massive \emph{INC task copies} (i.e., replicating task components inside or across switches) to ensure execution correctness, leading to unnecessary switch resource consumption. 

We propose \sysname, the \underline{R}esource-efficient \underline{INC} framework. Its key idea is to decrease INC task copies: \sysname replaces the sub-optimal manual decomposition of INC tasks with automatic decomposition that reduce inter-switch task copies via careful task analysis. Then it encodes constraints based on the characteristics of modern switches to eliminate intra-switch task copies. Also, \sysname offers a greedy-based heuristic that solves the problem in a near-optimal and timely manner. We have implemented \sysname on Tofino switches. Our experiments present that compared to state of the arts, \sysname can improve resource efficiency by 61\%. Also, applying \sysname to edge cloud networks built by a global service provider and an Internet service provider helps administrators deploy 0.7$\sim$5.1$\times$ more INC tasks. 
\end{abstract}
